---
title: "demo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ncbi)
set.seed(42)
```

## Overview

 * Find human membrane proteins
 * Pick a human membrane protein
 * Find related proteins
 * Align the protein sequences
 * Determine the topology of all protein sequences
 * Tally the mutations that have the same location in all topologies

## Find human membrane proteins

Either go to [https://www.ncbi.nlm.nih.gov/protein?term=(membrane%20protein)%20AND%20homo%20sapiens%5BPrimary%20Organism%5D](https://www.ncbi.nlm.nih.gov/protein?term=(membrane%20protein)%20AND%20homo%20sapiens%5BPrimary%20Organism%5D) or run:

```{r}
ids <- search_for_human_membrane_proteins()
ids
```

## Pick a human membrane protein

Pick a human membrane protein by clicking it on the
web interface.

In R, we pick a random one:

```{r}
id <- sample(x = ids, size = 1)
id
```

## Find related proteins

In the web interface, click on 'Run BLAST' to start blastp,
then run blastp and wait.

In R, we

 * Fetch the protein sequence
 * Run blastp on it

Fetch the protein sequence from the protein ID:

```{r}
sequence <- unname(fetch_sequence_from_protein_id(id))
sequence
```


 Run blastp on the protein sequence

```{r cache=TRUE}
blastp_result <- bio3d::blast.pdb(sequence)
```


```{r}
similar_subject_ids <- blastp_result$hit.tbl$subjectids

```

 * Click on 'Run BLAST', https://blast.ncbi.nlm.nih.gov/Blast.cgi?PAGE=Proteins&PROGRAM=blastp&BLAST_PROGRAMS=blastp&QUERY=BAA86974.1&LINK_LOC=protein&PAGE_TYPE=BlastSearch
 * BLAST and wait
 * Select the proteins that have 80% or more of the max score
 * Click 'Multiple alignment' to get COBALT multiple sequence alignment
 * Download the COBALT MSA alignment
 * Remove sequences that have deletions in the middle of the sequence
 * Determine the topology of all remaining sequences
 * Count mutations that have the same location in all topologies
